### 2012-10-11 abs.tex
Completion of draft of chapter 3

Chapter \ref{gradience} considers evidence from wordlikeness rating tasks. It is argued that intermediate well-formedness ratings are obtained whether or not the categories in question are graded. A primitive categorical model of wordlikeness using prosodic representations is outlined, and shown to predict English speakers' wordlikeness judgements at least as acccurately as state-of-the-art gradient wellformedness models. Once categorical effects are controlled for, gradient models are uncorrelated with well-formedness ratings.

>>>>

Chapter \ref{gradience} considers evidence from wordlikeness rating tasks. It is argued that intermediate well-formedness ratings are obtained whether or not the categories in question are graded. A primitive categorical model of wordlikeness using prosodic representations is outlined, and shown to predict English speakers' wordlikeness judgements at least as accurately as state-of-the-art gradient wellformedness models. Once categorical effects are controlled for, gradient models are uncorrelated with well-formedness ratings.

### 2012-10-11 pre.tex
Completion of draft of chapter 3

Similarly, theorists of lexical processing postulate that complex words are stored in memory to account for the facilitatory effect of whole word frequency on reaction times to complex words \citep[e.g.,][]{Alegre1999,Baayen1997a,Sereno1997}. But this effect of word frequency obtains regardless of whether or not whole word storage is postulated \citep{Taft2004b,LignosInPress}. Furthermore, in languages with rich agglutinative morphology, the role played by a whole word storage mechanism, should one be evidenced, would necessarily be quite marginal \citep{Hankamer1992,Chan2008}. According to one estimate, children acquiring American English hear 165,000 word tokens a week \citep{Swingley2007}. At that rate, it would take more than two months for a child to encounter the 1.5 milllion inflectional variants of a single verb in Archi \citep[467]{Kibrik1998},
%, cited in \citealt[122]{Bauer2001}), 
even if adult speech consisted of nothing but orderly recitation of the inflectional forms of this one verb, one after the other, without repetition.

@@

A strict application of this negative heuristic produces some interesting predictions. If speakers are shown to have internalize a phonotactic generalization, then there must be a phonological process to blame. One clear case where processes, and not merely restrictions on underlying representations, are implicated is in Quecha, where ejective co-occurrence restrictions are reflected in speakers' difficulties in producing nonce words containing multiple ejectives \citep{GallagherInPress}.

This negative heuristic also allows for the possibility of using psycholinguistic evidence to decide between competing phonological analyses. For instance, there is a long-standing debate concerning the representation of Sanskrit aspiration alternations like those represented by \emph{bodhati}-\emph{bhotsyati} `he wakes-he will wake'. One analysis, going back to the ancient grammarian Pāṇini \citep{Sag1974} and to \citet[\S141f.]{Whitney1889}, posits an underlying representation /budh-/ with aspiration shifting leftward in certain contexts: modern proponents of this analysis include \citet{Borowsky1983}, \citet[][59f.]{Hoenigswald1965}, \citet{Kaye1985}, \citet{Sag1974,Sag1976} \citet{Schindler1976}, \citet{Stemberger1980}, and \citet[][\S141f.]{Whitney1889}. An alternative analysis posits an underlying representation /bhudh-/ and an apsirate dissimilation process (\citealt{Anderson1970}, \citealt{Hoard1975}, \citealt[\S3.2]{Kiparsky1965}, \citealt{Phelps1973}, \citealt{Phelps1975b}, \citealt[109f.]{Zwicky1965}). It is not my intention to adjudicate between these competing analyses, or to evaluate the claim that both accounts are deeply flawed \citep{Janda1989}, but simply to note that they make different predictions under the theory proposed here. While the former, aspirate shift analysis denies the existence of diaspirate roots, this fact lacks synchronic motivation, so the co-occurrence restriction may go unlearned. On the other hand, under the aspirate dissimilation account, underlying diaspirate roots exist but speakers internalize synchronic processes responsible for their absence on the surface.

>>>>

Similarly, theorists of lexical processing postulate that complex words are stored in memory to account for the facilitatory effect of whole word frequency on reaction times to complex words \citep[e.g.,][]{Alegre1999,Baayen1997a,Sereno1997}. But this effect of word frequency obtains regardless of whether or not whole word storage is postulated \citep{Taft2004b,LignosInPress}. Furthermore, in languages with rich agglutinative morphology, the role played by a whole word storage mechanism, should one be evidenced, would necessarily be quite marginal \citep{Anderson1988a,Hankamer1992,Chan2008}. According to one estimate, children acquiring American English hear 165,000 word tokens a week \citep{Swingley2007}. At that rate, it would take more than two months for a child to encounter the 1.5 milllion inflectional variants of a single verb in Archi \citep[467]{Kibrik1998},
%, cited in \citealt[122]{Bauer2001}), 
even if adult speech consisted of nothing but orderly recitation of the inflectional forms of this one verb, one after the other, without repetition.

@@

A strict application of this negative heuristic produces some interesting predictions. If speakers are shown to have internalize a phonotactic generalization, then there must be a phonological process to blame. One clear case where processes, and not merely restrictions on underlying representations, 
is where co-occurrence restrictions cause difficulties in producing nonce words violating those restrictions
\citep{Rose2007,GallagherInPress}

are implicated is in Quecha, where ejective co-occurrence restrictions are reflected in speakers' difficulties in producing nonce words containing multiple ejectives \citep{GallagherInPress}.

This negative heuristic also allows for the possibility of using psycholinguistic evidence to decide between competing phonological analyses. For instance, there is a long-standing debate concerning the representation of Sanskrit aspiration alternations like those represented by \emph{bodhati}-\emph{bhotsyati} `he wakes-he will wake'. One analysis, going back to the ancient grammarian Pāṇini \citep{Sag1974} and to \citet[\S141f.]{Whitney1889}, posits an underlying representation /bud\asp{}-/ with aspiration shifting leftward in certain contexts: modern proponents of this analysis include \citet{Borowsky1983}, \citet[][59f.]{Hoenigswald1965}, \citet{Kaye1985}, \citet{Sag1974,Sag1976} \citet{Schindler1976}, \citet{Stemberger1980}, and \citet[][\S141f.]{Whitney1889}. An alternative analysis posits an underlying representation /b\asp{}ud\asp{}-/ and an apsirate dissimilation process (\citealt{Anderson1970}, \citealt{Hoard1975}, \citealt[\S3.2]{Kiparsky1965}, \citealt{Phelps1973}, \citealt{Phelps1975b}, \citealt[109f.]{Zwicky1965}). It is not my intention to adjudicate between these competing analyses, or to evaluate the claim that both accounts are deeply flawed \citep{Janda1989}, but simply to note that they make different predictions under the theory proposed here. While the former, aspirate shift analysis denies the existence of diaspirate roots, this fact lacks synchronic motivation, so the co-occurrence restriction go unlearned. On the other hand, under the aspirate dissimilation account, underlying diaspirate roots exist but speakers internalize synchronic processes responsible for their absence on the surface.
